Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-05-25 latex/afm-cs-main.tex
Add the mimo FRF figure.

\documentclass[twocolumn,twoside]{IEEEtran/IEEEtran}
% \documentclass[defaultstyle,11pt]{IEEETran}
% Lucy says to look at:
% float_page_fraction
% tex_page_fraction
% https://tex.stackexchange.com/questions/35125/how-to-use-the-placement-options-t-h-with-figures#35130
% \renewcommand\floatpagefraction{0.5} %% default: 0.5
% \renewcommand\topfraction{0.7} % default: 0.7
% \renewcommand*\textfraction{.05}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs}
% \usepackage{amsthm}
\usepackage[percent]{overpic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{catchfilebetweentags} % for data input
\usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath, dsfont, bbold}
% \usepackage{algpseudocode,algorithm,algorithmicx}
\usepackage[linesnumberedhidden,ruled]{algorithm2e}
\usepackage{placeins}
\usepackage{todonotes}

@@

\begin{document}
\title{High-speed atomic force microscopy through $\mu$-path sampling}

\author{Roger A. Braker and Yufan Luo and Lucy Y. Pao and Sean B. Andersson
  \thanks{The authors are with the Dept. of Electrical, Computer, and Energy
    Engineering at the University of Colorado, 425 UCB, Boulder, CO 80309,
    United States. Phone: +1 (303) 492-2360. Fax: +1 (303) 492-2758. R. A.
    Braker (corresponding author roger.braker@colorado.edu) is a graduate
    student and L.Y. Pao (pao@colorado.edu) is the Richard \& Joy Dorf
    Professor.} \thanks{This work was supported in part by the US National
    Science Foundation (NSF Grant CMMI-1234980) and Agilent Technologies, Inc.}
}

@@

In this work, we use three reconstruction algorithms to generate the final
surface image. The first one comes from the field of compressive sensing (CS).
CS is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, of the fact that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the following observation equation,
\begin{equation}\label{op:observation}
  y = \Phi x = \Phi\Psi\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^m$ is the observation vector, $\Phi$ is an
$m\times n$ matrix defining the measurements, $\Psi$ is an $n\times n$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $\Psi$. In
general, $m\ll n$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix. Note that the
symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
They are reused here as they are standard notation in the CS literature; their
specific meaning throughout the paper should be clear from context.

In the AFM application, the probe can only measure a single pixel at a time.
This implies that $\Phi$ is a sparse matrix with each row having only one
nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
the measurement matrix $\Phi$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $\Phi$ (the measurements)
``spreads out'' in the domain of $\Psi$ \cite{candes2007sparsity}. In practice,
the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
mutual coherence between the basis and the required structure of the AFM sensing
matrices and providing a high sparsity of typical AFM sample images. Therefore,
for concreteness, in this work we use the DCT as the sparsity basis $\Psi$.

One common realization of the CS-based reconstruction problem, known as basis
pursuit with denoising (BPDN), is given by the following optimization problem,
\begin{equation}\label{op:bp}
  \begin{aligned}
	\min_{x} \left \| \Psi^{-1}x \right \|_1\quad \text{subject to}\quad \|\Phi
    x - y\|_2 < \sigma,
  \end{aligned}
\end{equation}
where $\| \cdot \|_1$ and $\| \cdot \|_2$ denote $l_1$ and $l_2$ norms,
respectively, and $\sigma$ represents some measure of the signal noise such as
its variance. This problem essentially searches for the sparsest signal from all
the candidates that match the measurements. While BPDN is a computationally
demanding algorithm, particularly for large images, it in general provides
accurate reconstructions. In this work, we use the package
$l_1$-magic~\cite{l1magic} to solve the BPDN problem. More efficient greedy
algorithms have also been developed. One of these, Simplified Matching Pursuit
(SMP), was created by two of the authors and was designed specifically for the
sampling matrices in the AFM setting \cite{Luo:2015tu}.

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$\Phi$ and the sparsity basis $\Psi$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times. As a result, the second
algorithm we consider is a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). In order to mitigate the vertical artifacts, BPVV
adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\begin{equation}\label{op:bp_tv}
  \begin{aligned}
	\min_{x} \left \| \Psi^{-1}x \right \|_1 + \epsilon \left \| \nabla_v x
    \right \|_1 \, \text{subject to} \, \| \Phi x - y \|_2 < \sigma,
  \end{aligned}
\end{equation}
where ${\nabla_v x=\text{vec}(\nabla_v X)}$ is the discrete gradient in the
vertical ($y$) direction and
% \textcolor{red}{
\begin{equation}
  (\nabla_v X)_{i,j} = 
  \begin{cases}
    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
  \end{cases}
\end{equation}

@@

  \Initialize{$x = d_y = w = b_y = b_w = k = 0$, $y_0=y$ sampled pixels}
  \While{$\left \|\Phi x^k - y^k \right \|_2 \ge \sigma$} {
    % $x^{k+1} = x^{k}$\\
    \For{$i= 1$ \KwTo $N$} {
      $p\leftarrow\mu\Phi^Ty^k+\lambda\nabla_v^T\left(d_y-b_y\right)+\gamma\Psi\left(w-b_w\right)$\\
      $x^{k+1}\leftarrow \left(\mu\Phi^{T}\Phi+\lambda\nabla_v^T\nabla_v+\gamma I\right)^{-1}p$\\
      $d_y\leftarrow \text{shrink}(\nabla_vx^{k+1}+b_y,1/\lambda)$\\
      $w\leftarrow \text{shrink}\left(\Psi^{-1}x^{k+1}+b_w,1/\gamma\right)$\\
      $b_y\leftarrow b_y+\left(\nabla_vx^{k+1}-d_y\right)$\\
      $b_w\leftarrow b_w+\left(\Psi^{-1}x^{k+1}-w\right)$\\
    }
    $y^{k+1} = y^k + y - \Phi x^{k+1}$\\
    $k \leftarrow k + 1$\\
  } \Output{Reconstruction $x^k$}
  \caption{Split Bregman BPVV}
  \label{ag:BPTV}
\end{algorithm}
\todo{Modify this for NESTA}

In \eqref{op:bp_tv}, $\left \| \nabla_v x \right \|_1$ is the total variation of
the signal in the vertical direction and $\epsilon$ is a weighting parameter
which in this work is taken to be unity. The description of BPVV in
\eqref{op:bp_tv} can be viewed as the combination of CS and inpainting
(described below), in which the first term seeks a sparse solution while the
second term tries to diffuse pixel information. To solve the optimization
problem in \eqref{op:bp_tv} we use the split Bregman method
\cite{goldstein2009split}. The resulting algorithm is described in
Algorithm~\ref{ag:BPTV} where $\mu, \lambda, \gamma$ are scalar penalty
parameters that influence the convergence of the algorithm (though not the
solution found) and
\begin{equation}\label{df:shrink}
  \text{shrink}(x,\gamma) = \frac{x}{|x|}\max\left(|x|-\gamma,0\right),
\end{equation}
where all operations are element-wise.

@@

One cause for such different gains is variation in the length of the cantilever
(and possibly how the laser was adjusted). This is illustrated in
Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
rests on the surface of some specimen with a nominal angle of $\theta$. In this
drawing, the laser is perpendicular to the sample surface. Given a vertical
perturbation $\Delta z$, we have that
\begin{equation}
  \Delta \alpha \approx \frac{d}{h} \Delta z,
\end{equation}
where $d$ is the distance from the cantilever to the detector and
$\Delta \alpha$ is the change in position of the incident laser spot on the
detector. Thus, given the same change in the vertical position, we will see a
larger change in the deflection signal for a shorter cantilever. In other words,
a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
function.
\begin{figure}
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
    \caption{FRFs of three different cantilevers, showing substantial
      differences in the DC-gain and smaller, but still significant differences
      the frequency of the modes.}
    \label{fig:z_evolution}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
    \caption{Schematic drawing of how the length of the cantilever affects the
      $z$-axis gain.}
    \label{fig:z_axis_gain}
  \end{minipage}
\end{figure}

Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
the bending mode for three different cantilevers. Cantilevers (A) and (B) are
both AppNano SICON cantilevers and have a nominal length of 450 microns.
Cantilever (C) is an NCLR and has a nominal length of 225 microns.
Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
the manufacture does not provide a tolerance on the nominal length, so it is
difficult to tease out whether that variation is due to manufacturing
variability or other factors not explained by this analysis.

Notably, the frequency of the pole and zero do appear to shift and our inversion
scheme is not robust to this. To deal with this, I have built a (mostly)
automated system ID routine into the imaging software. This routine is a
specialized version of the techniques described previously in
Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
frequency range spanning 180~Hz to 240~Hz (the same set of points as in
Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
2-zero transfer function model of the form
\begin{equation*}
  \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
\end{equation*}
is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
This is done inside the LabView VI by calling a custom DLL, which leverages
CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
a stable fit, the optimization enforces the necessary conditions that
\begin{align*}
  |a_1| &< 2, \quad  |a_o| < 1\\
  |b_1| &< 2, \quad  |b_o| < 1.
\end{align*}
The routine then checks that both the poles and zeros are indeed stabile, saves
the data to a JSON file and passes the transfer function parameters into the
imaging portion of the application which finally uploads the parameters into the
FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
previously saved JSON file.

One of the benefits of this approach is that the DC-gain of the transfer
function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
re-tuning the control system after changing tips far easier to non-existent. The
benefit to automating the process is that it drastically reduces the friction
required to obtain an up-to-date compensator, which means that an up-to-date
compensator is more likely to be used~\cite{abramovitch_25years_2015}.

Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
$D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
will get a lot of wiggles in the resulting signal. Rather, we need to take only
the output of the integrator to represent the surface.
% \begin{figure}
%   \centering
%   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop with the inverse
%   compensator. }
%   \label{fig:afm_bd_dinv}
% \end{figure}
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=r_{Z,\textrm{up}}$.}
  \label{fig:afm_bd_dinv_final}
\end{figure*}

It should be noted that this control is sufficient to eliminate the limit-cycle
behavior described in Section~\ref{sec:aproachspeed}:

% \begin{figure}[tbhp!]
%   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
%   \caption{The $z$-piezo movement is driven by switching between feedback from
%   the $z$-axis position signal and from the deflection signal. The shaded area
%   represents the digital control system, while the non-shaded region is the
%   physical system.}
%   \label{fig:zMultiplex_anderssonLab}
% \end{figure}

As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
position sensor (when the tip is off the surface) and the deflection signal
(when the tip is engaged). The difference equation associated with
\eqref{eqn:dzI} for the $z$-axis is
\begin{equation}
  u_z(k) = K_Ie(k) + u_z(k-1).
  \label{eqn:intdiff}
\end{equation}

In the $z$-axis position control mode, the $z$-axis position is controlled to a
fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
The difference between the measured $z$-axis position and $z_{ref}$,
${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
control mode, when the tip is in contact with the sample, the deflection signal
is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
The sample surface acts as a disturbance to the control loop. Therefore, the
$z$-axis position measurements can be taken to represent the surface topography
of the sample. In this case, the difference between the measured deflection and
$l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.

We note that the $z$-axis control described here operates the AFM in constant
force mode during imaging. It is straightforward to perform scanning under
different AFM modes, such as tapping mode, simply by adjusting the signals and
control involved in the vertical loop.

>>>>

\documentclass[twocolumn,twoside]{IEEEtran/IEEEtran}
% \documentclass[defaultstyle,11pt]{IEEETran}
% Lucy says to look at:
% float_page_fraction
% tex_page_fraction
% https://tex.stackexchange.com/questions/35125/how-to-use-the-placement-options-t-h-with-figures#35130
% \renewcommand\floatpagefraction{0.5} %% default: 0.5
% \renewcommand\topfraction{0.7} % default: 0.7
% \renewcommand*\textfraction{.05}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs}
% \usepackage{amsthm}
\usepackage[percent]{overpic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{catchfilebetweentags} % for data input
\usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath, dsfont, bbold}
% \usepackage{algpseudocode,algorithm,algorithmicx}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{placeins}
\usepackage{todonotes}

@@

\begin{document}
\title{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling}

\author{Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean B. Andersson
  \thanks{The authors are with the Dept. of Electrical, Computer, and Energy
    Engineering at the University of Colorado, 425 UCB, Boulder, CO 80309,
    United States. Phone: +1 (303) 492-2360. Fax: +1 (303) 492-2758. R. A.
    Braker (corresponding author roger.braker@colorado.edu) is a graduate
    student and L.Y. Pao (pao@colorado.edu) is the Richard \& Joy Dorf
    Professor.} \thanks{This work was supported in part by the US National
    Science Foundation (NSF Grant CMMI-1234980) and Agilent Technologies, Inc.}
}

@@

In this work, we use three reconstruction algorithms to generate the final
surface image. The first one comes from the field of compressive sensing (CS).
CS is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, of the fact that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the following observation equation,
\begin{equation}\label{op:observation}
  y = R x = RU\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
$m\times n$ matrix defining the measurements, $U$ is an $n\times n$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
general, $m\ll n$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix.

The symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
They are reused here as they are standard notation in the CS literature; their
specific meaning throughout the paper should be clear from context.

In the AFM application, the probe can only measure a single pixel at a time.
This implies that $R$ is a sparse matrix with each row having only one
nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
the measurement matrix $U$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}. In practice,
the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
mutual coherence between the basis and the required structure of the AFM sensing
matrices and providing a high sparsity of typical AFM sample images. In the following,
we assume that $U^TU=I$, though in the simulation and experimental results, we take
$U$ as the DCT basis.

One common realization of the CS-based reconstruction problem, known as basis
pursuit with denoising (BPDN), is given by the following optimization problem,
\begin{equation}
  \min_{x} \left \| U^Tx \right \|_1 \quad
  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
\end{equation}
  where $\| \cdot \|_1$ and $\| \cdot \|_2$ denote $l_1$ and $l_2$ norms,
respectively, and $\sigma$ represents some measure of the signal noise such as
its variance. This problem essentially searches for the sparsest signal from all
the candidates that match the measurements. While BPDN is a computationally
demanding algorithm, particularly for large images, it in general provides
accurate reconstructions.

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
As a result, the second
algorithm we consider is a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). In order to mitigate the vertical artifacts, BPVV
adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to

\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} |U^Tx|_1 + \alpha_v|D_vx|_1 + \alpha_h|D_hx|_1  \label{op:bp_tv}
  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
\end{align}
where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
discrete gradient in the vertical (resp., horizontal) direction and
\begin{align*}
  (\nabla_v X)_{i,j} = 
  \begin{cases}
    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
  \end{cases}\\
  (\nabla_h X)_{i,j} = 
  \begin{cases}
    X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
    0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
  \end{cases}
\end{align*}
In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction. The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
and inpainting (described below), in which the first term seeks a sparse solution while the
last two terms try to diffuse pixel information.
To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
\begin{equation*}
  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
\end{equation*}
where 
\begin{equation*}
W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
\end{equation*}
One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
\begin{equation}
  f_{\mu} = \max_{u\in Q_d} \left\langle u,
    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
\end{equation}
The gradient of \eqref{eqn:fcn_prox} is given by
\begin{equation*}
  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
\end{equation*}
where
\begin{equation*}
  (u_{\mu}(x))[i] = 
\begin{cases}
    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
    \text{sgn}(W x[i]), & \text{else}.
  \end{cases}
\end{equation*}

@@

  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
    % $x^{k+1} = x^{k}$\\
  \While{$\mu < \mu_{\textrm{final}}$ } {
    $k=0$\\
      \While{$\Delta f_{\mu} > \delta$} {
        $\alpha_k = \frac{1}{2}(k+1)$ \\
        $\tau_k = \frac{2}{k+3}$ \\
        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
        $k \leftarrow k + 1$\\
      }
      $x_0 = x_k$\\
      $\mu = \gamma \mu$\\
      $L_{\mu} = (1/\mu)||W||^2_2$
    }
  \Output{Reconstruction $x_k$}
  \caption{NESTA algorithm}
  \label{ag:BPTV}
\end{algorithm}
In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
\begin{equation}
\bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
\end{equation}
The sub-problems in lines 6 and 7 have the form
\begin{equation}
  p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
\end{equation}
for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
\begin{align}
  \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
  q &= r - L^{-1}g\\
  p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
\end{align}

@@

\begin{figure*}
  \centering
  \includesvg[width=1\textwidth]{figures/MIMO_CL_uxuy.svg}
  \caption{MIMO closed and open loop FRFs, showing the dramatic affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward compensators are used for the $X$ and $Y$ axes.}
  \label{fig:mimo_frf_uxuy}
\end{figure*}

% One cause for such different gains is variation in the length of the cantilever
% (and possibly how the laser was adjusted). This is illustrated in
% Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
% rests on the surface of some specimen with a nominal angle of $\theta$. In this
% drawing, the laser is perpendicular to the sample surface. Given a vertical
% perturbation $\Delta z$, we have that
% \begin{equation}
%   \Delta \alpha \approx \frac{d}{h} \Delta z,
% \end{equation}
% where $d$ is the distance from the cantilever to the detector and
% $\Delta \alpha$ is the change in position of the incident laser spot on the
% detector. Thus, given the same change in the vertical position, we will see a
% larger change in the deflection signal for a shorter cantilever. In other words,
% a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
% function.
% \begin{figure}
%   \begin{minipage}[t]{.46\textwidth}
%     % L B R T
%     \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
%     \caption{FRFs of three different cantilevers, showing substantial
%       differences in the DC-gain and smaller, but still significant differences
%       the frequency of the modes.}
%     \label{fig:z_evolution}
%   \end{minipage}
%   \hfill
%   \begin{minipage}[t]{.46\textwidth}
%     % L B R T
%     \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
%     \caption{Schematic drawing of how the length of the cantilever affects the
%       $z$-axis gain.}
%     \label{fig:z_axis_gain}
%   \end{minipage}
% \end{figure}

% Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
% the bending mode for three different cantilevers. Cantilevers (A) and (B) are
% both AppNano SICON cantilevers and have a nominal length of 450 microns.
% Cantilever (C) is an NCLR and has a nominal length of 225 microns.
% Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
% the manufacture does not provide a tolerance on the nominal length, so it is
% difficult to tease out whether that variation is due to manufacturing
% variability or other factors not explained by this analysis.

% Notably, the frequency of the pole and zero do appear to shift and our inversion
% scheme is not robust to this. To deal with this, I have built a (mostly)
% automated system ID routine into the imaging software. This routine is a
% specialized version of the techniques described previously in
% Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
% frequency range spanning 180~Hz to 240~Hz (the same set of points as in
% Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
% quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
% 2-zero transfer function model of the form
% \begin{equation*}
%   \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
% \end{equation*}
% is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
% This is done inside the LabView VI by calling a custom DLL, which leverages
% CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
% Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
% a stable fit, the optimization enforces the necessary conditions that
% \begin{align*}
%   |a_1| &< 2, \quad  |a_o| < 1\\
%   |b_1| &< 2, \quad  |b_o| < 1.
% \end{align*}
% The routine then checks that both the poles and zeros are indeed stabile, saves
% the data to a JSON file and passes the transfer function parameters into the
% imaging portion of the application which finally uploads the parameters into the
% FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
% previously saved JSON file.

% One of the benefits of this approach is that the DC-gain of the transfer
% function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
% re-tuning the control system after changing tips far easier to non-existent. The
% benefit to automating the process is that it drastically reduces the friction
% required to obtain an up-to-date compensator, which means that an up-to-date
% compensator is more likely to be used~\cite{abramovitch_25years_2015}.

% Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
% We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
% $D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
% If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
% will get a lot of wiggles in the resulting signal. Rather, we need to take only
% the output of the integrator to represent the surface.
% % \begin{figure}
% %   \centering
% %   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
% %   \caption{Block diagram of the $Z$-axis control loop with the inverse
% %   compensator. }
% %   \label{fig:afm_bd_dinv}
% % \end{figure}
% \begin{figure*}[t]
%   \centering
%   \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
%     for decision index $i\in\{0,1,5\}$, which correspond to states such that
%     $r_Z=r_{Z,\textrm{up}}$.}
%   \label{fig:afm_bd_dinv_final}
% \end{figure*}

% It should be noted that this control is sufficient to eliminate the limit-cycle
% behavior described in Section~\ref{sec:aproachspeed}:

% % \begin{figure}[tbhp!]
% %   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
% %   \caption{The $z$-piezo movement is driven by switching between feedback from
% %   the $z$-axis position signal and from the deflection signal. The shaded area
% %   represents the digital control system, while the non-shaded region is the
% %   physical system.}
% %   \label{fig:zMultiplex_anderssonLab}
% % \end{figure}

% As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
% the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
% position sensor (when the tip is off the surface) and the deflection signal
% (when the tip is engaged). The difference equation associated with
% \eqref{eqn:dzI} for the $z$-axis is
% \begin{equation}
%   u_z(k) = K_Ie(k) + u_z(k-1).
%   \label{eqn:intdiff}
% \end{equation}

% In the $z$-axis position control mode, the $z$-axis position is controlled to a
% fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
% The difference between the measured $z$-axis position and $z_{ref}$,
% ${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
% control mode, when the tip is in contact with the sample, the deflection signal
% is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
% The sample surface acts as a disturbance to the control loop. Therefore, the
% $z$-axis position measurements can be taken to represent the surface topography
% of the sample. In this case, the difference between the measured deflection and
% $l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.

% We note that the $z$-axis control described here operates the AFM in constant
% force mode during imaging. It is straightforward to perform scanning under
% different AFM modes, such as tapping mode, simply by adjusting the signals and
% control involved in the vertical loop.
